Prediction of 2024 US election ...

### 2024-11-02 paper/paper.qmd
update measurement in paper and simulation

FiveThirtyEight’s polling measurement approach transforms raw polling data from multiple sources into one dataset by following a structured, multi-step process. First, it collects polling data from a variety of sources that meet its methodological and ethical standards. According to @radcliffe_538s_2023, polls included must disclose key details, such as the pollster’s name, survey dates, and the sampled population. FiveThirtyEight also excludes any hypothetical matchups or polls asking for general support of a party. The average result is reflected in the 'pct' column.

Next, FiveThirtyEight applies a series of adjustments to the data to account for sample size, timing, and pollster quality. As stated by @silver_polls_2008, the polls are weighted more heavily if they associate with larger sample. The sample size is documented in the data set as 'sample_size'. Poll recency is another critical factor, with newer polls weighted more to reflect current opinion trends. The 'pollscore' in the dataset is an indicator of pollster transparency and reliability in their methodology, according to @morris_trump_2024.

Further adjustments address polling biases, such as “house effects” (systematic leanings toward a particular candidate) and the mode of polling. Likely-voter adjustment are applied to all polls of registered voters and adults. Third party adjustment are applied to polls that only consider Biden and Trump as the candidates. Polls from partisan sources are included, but FiveThirtyEight applies a correction to counteract inherent biases [@morris_trump_2024].

>>>>

The dataset we obtained from @fivethirtyeight is accumulated from multiple polls and surveys. According to FiveThirtyEight, they aggregate polling data conducted by other firms and organizations that meets their methodological and ethical standards [@morris_trump_2024]. The dataset contains a list of questions in polls and surveys and their results. When a new poll is conducted, the poll is appended to the dataset. FiveThirtyEight assign the poll a poll_id, and each question is assigned a question_id.

In each of the polls recorded by FiveThirtyEight, all options of each question are recorded in candidate_names, while the proportion of respondents choosing that option is recorded in pct as a percentage. The pct is our primary response variable.

There are limitations in these measurements. The differences in sampling methods, wording in survey questions and systematic biases are all reflected in the outcome [@radcliffe_538s_2023]. Thus, in the dataset, FiveThirtyEight includes other variables, such as pollscore and sample_size for their prediction model in addition to the polling results for transparency and accuracy. As an example, pollscore indicates the pollster’s reliability rating, a low pollscore indicates a higher reliability rating [@silver_polls_2008].

These variables combined allow researchers to reliably analyze and predict the 2024 US election result over time.
